---
title: "Prediction using Unsupervised ML"
author: "Ayantika Maity"
output: html_document
---
**Query: Predict the optimum number of clusters and represent it visually.**

The iris dataset consists of 4 features(sepal length and sepal width, petal length and petal width) and 3 species of iris.

We will use K-mean clustering algorithm for this task.

Programming language used: R

**Importing Dataset**
```{r}
library(readr)
df <- read.csv("C:/Users/Ayantika Maity/Downloads/Iris.csv")
head(df)
```

**Data Preprocessing**
```{r}
dim(df)
```
**Structure of data**
```{r}
str(df)
summary(df)
```
**Missing values**
```{r}
colSums(is.na(df))
```
There is no missing value, so no need of data cleaning.

Now Clustering Iris dataset without "ID" and "Species" column.
```{r}
newdf<- df[,2:5]
head(newdf)
class <- df[,6]
```

**Optimum number of Clusters**

Let us use the elbow method to find the optimum number of clusters. 
```{r echo=TRUE, message=FALSE}
library(factoextra)
```
```{r}
fviz_nbclust(newdf, kmeans, method = "wss") + 
geom_vline(xintercept = 3, linetype=2)
```
  
From the graph, it is observed that the elbow point is at k=3 after which the graph becomes linear. The number of optimum clusters for the data set is 3.

As we can see that with a increase in the number of clusters, the WSS value decreases. And we see, after k=3, the drop of WSS is minimal.

**Model**

Lets create a model with 3 clusters.  
```{r echo=TRUE}
library(stats)
result <- kmeans(newdf, centers=3)
class(result)
table(class)
```
Here we are comparing prediction with actual species.

Size of the clusters  
```{r echo=TRUE}
result$size
```
We can also look at which clusters do the observations belong to.  
```{r echo=TRUE}
result$cluster
table(class,result$cluster)
```

### **Visualization**
```{r echo=TRUE}
plot(df[,2:5], col=result$cluster)
```
  
The above plot clearly shows the 3 clusters. 
We can also view the plots seperately as follows :   
```{r echo=TRUE}
df$cluster <- as.character(result$cluster)
```
```{r echo=TRUE}
library(ggplot2)
```
```{r echo=TRUE}
ggplot() +
  geom_point(data = df, 
             mapping = aes(x = SepalLengthCm, 
                           y = SepalWidthCm, 
                           colour = cluster)) +
  labs ( title = '\nSepalLength(in_cm) vs SepalWidth(in_cm)\n') +
  theme_light()
```

```{r echo=TRUE}
ggplot() +
  geom_point(data = df, 
             mapping = aes(x = PetalLengthCm, 
                           y = PetalWidthCm, 
                           colour = cluster)) +
  labs ( title = '\nPetalLength(in_cm) vs PetalWidth(in_cm)\n') +
  theme_light()
```

**Thank you**
